\documentclass[a4paper,10pt]{article}

\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}

% Title Page
\title{Baby Brain Toolkit}
\author{Fbrain ERC project: Computational Anatomy of Fetal Brain}


\begin{document}
\maketitle
\tableofcontents
%\begin{abstract}
%\end{abstract}

\section{Introduction}

BTK stands for Baby Brain Toolkit. This toolkit is developed in the context of
the Fbrain ERC project: ``Computational Anatomy of Fetal
Brain''\footnote{http://lsiit-miv.u-strasbg.fr/miv/index.php?contenu=erc}. 
Studies about brain maturation aim at providing a better understanding of brain
development and links between brain changes and cognitive development. Such
studies are of great interest for diagnosis help and clinical course of
development and treatment of illnesses. Several teams have begun to make 3D maps
of developing brain structures from children to young adults. However, working
out the development of fetal and neonatal brain remains an open issue. This
project aims at jumping over several theoretical and practical barriers and at
going beyond the formal description of the brain maturation thanks to the
development of a realistic numerical model of brain aging.

\subsection{Copyright}
This software is governed by the CeCILL-B license under French law and
abiding by the rules of distribution of free software.  You can  use, 
modify and/ or redistribute the software under the terms of the CeCILL-B
license as circulated by CEA, CNRS and INRIA at the following URL
"http://www.cecill.info". 

As a counterpart to the access to the source code and rights to copy,
modify and redistribute granted by the license, users are provided only
with a limited warranty  and the software's author,  the holder of the
economic rights,  and the successive licensors  have only  limited
liability. 

In this respect, the user's attention is drawn to the risks associated
with loading,  using,  modifying and/or developing or reproducing the
software by the user in light of its specific status of free software,
that may mean  that it is complicated to manipulate,  and  that  also
therefore means  that it is reserved for developers  and  experienced
professionals having in-depth computer knowledge. Users are therefore
encouraged to load and test the software's suitability as regards their
requirements in conditions enabling the security of their systems and/or 
data to be ensured and,  more generally, to use and operate it in the 
same conditions as regards security. 

\subsection{Installation}

\subsubsection{Dependencies}

Baby Brain Toolkit (BTK) needs the following packages:
\begin{itemize}
 \item CMake (www.cmake.org), Tclap (tclap.sourceforge.net), OpenMP (openmp.org), VTK (www.vtk.org), ANN (www.cs.umd.edu/\string~mount/ANN). These libraries can be installed using the following command line: 
 \begin{itemize}
 \item for debian-based distributions: \texttt{apt-get install cmake cmake-curses-gui libtclap-dev libgomp1 libvtk5-dev libann-dev}
 \item for MacOSX using macports: \texttt{port install cmake tclap vtk5 libANN}
 \end{itemize}
 \item Install Git: this library can be installed using the following command line : 
 \begin{itemize}
 \item for debian-based distribution: \texttt{apt-get install git-core}
 \item for MacOSX using macports: \texttt{port install git-core}
 \end{itemize}
 \item Insight Toolkit (ITK) version 4:
\begin{verbatim}
git clone git://itk.org/ITK.git
mkdir ITK-build
cd ITK-build
ccmake ../ITK/
\end{verbatim}
This will bring up the CMake configuration screen. Press \texttt{[c]} for configure and then use \texttt{[t]} to toggle the advanced mode. Make the following changes:
\begin{verbatim}
BUILD_TESTING = OFF
CMAKE_BUILD_TYPE = Release
ITK_USE_REVIEW = ON
ITK_BUILD_ALL_MODULES = ON
\end{verbatim}
Then press \texttt{[c]} to configure and \texttt{[g]} to generate the make file. Finally, type \texttt{make} at the prompt to obtain the final build of ITK.

\end{itemize}

\subsubsection{Download and compile the BTK sources}
\begin{itemize}
 \item Get the BTK sources: \texttt{git clone https://github.com/rousseau/fbrain.git }
 \item Then:
\begin{verbatim}
mkdir fbrain-build
cd fbrain-build
ccmake ../fbrain
make
\end{verbatim}
\end{itemize}

Most of the programs of the BTK suite use the OpenMP library for multi-threading
purpose. The number of cores used can be tuned using the following command line
(in this example, 4 cores will be used): \texttt{export OMP\_NUM\_THREADS=4}
\input{pipeline}
\input{app}
\input{utilities}

\section*{Acknowledgment}
\small{The research leading to these results has received funding from the
European Research Council under the European Community’s Seventh Framework
Programme (FP7/2007-2013 Grant Agreement no. 207667).}

\bibliographystyle{plain}
\bibliography{btk.bib}

\end{document}
